### 2019-11-28 paper/acks.tex
Abstract and conclusion added

Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the NNSA Office of Defense Nuclear Nonproliferation R\&D through the Consortium for Verification Technologies and the Consortium for Nonproliferation Enabling Capabilities,  the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

>>>>

Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

### 2019-11-28 paper/methods.tex
Abstract and conclusion added

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The \gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power of 2250 MW$_{th}$. The 
design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
\cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential} after modifying the geometry to 
control the positive temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
geometry is described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
\cite{li_optimization_2018,ashraf2019whole_core}. The active zone of the \gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile materials). Three different types of initial fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) elements from \gls{LWR} LWR \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, respectively.
The liquid fuel salt circulates continuously through the fuel tubes that pierce the graphite hexagonal 
prisms. The active zone is surrounded by axial and radial graphite reflectors to minimize the neutron leakage. Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of a Hastelloy N alloy. The main 
characteristics of the \gls{SD-TMSR} are summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | l}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_4$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Since the total quantity and distribution of the SD-TMSR control assemblies are unknown, we proposed an original distribution as a starting point of this analysis. We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods (cluster) can move together as one group. Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the four control rods. The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.

@@

The initial calculation state of the SD-TMSR is identified by normal operation conditions (see Table~\ref{tab:table1}) and fully withdrawn control rods clusters. In this case, the control rods are located above the upper plenum as shown in Figure~\ref{fig:core_26}. To validate the proposed control rods system we adopted the same operation conditions (as in the initial case) and changed the position of the control rod clusters along $Z$ direction. The main calculated parameters including reactivity, control rod worth, and interference effects (shadowing effects) will describe in the following parts.

@@

The control rod worth (CRW) is the amount of negative reactivity that associated with the control rod insertion. The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of i$^{th}$ CR, $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after i$^{th}$ CR insertion \cite{vcerba2017optimization}.

>>>>

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The \gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power of 2,250 MW$_{th}$. The 
design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
\cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential} after modifying the geometry to 
control the positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
\cite{li_optimization_2018,ashraf2019whole_core}. The active zone of the \gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile materials), and $N$ is dependent on the chosen fissile material and the thermochemical state of the liquid fuel salt. Three different types of initial fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, respectively.
The liquid fuel salt circulates continuously through the fuel tubes that pierce the graphite hexagonal 
prisms. The active zone is surrounded by axial and radial graphite reflectors to minimize the neutron leakage. Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of a Hastelloy N alloy. The main 
characteristics of the \gls{SD-TMSR} are summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Since the total quantity and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis. We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods (cluster) can move together as one group. Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods. The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.

@@

The initial calculation state of the SD-TMSR is identified by normal operation conditions (see Table~\ref{tab:table1}) and fully withdrawn control rods clusters. In this case, the control rods are located above the upper plenum as shown in Figure~\ref{fig:core_26}. To validate the proposed control rods system we adopted the same operation conditions (as in the initial calculation state) and changed the position of the control rod clusters along $Z$ direction. The main calculated parameters including reactivity, control rod worth, and interference effects (shadowing effects) will describe in the following parts.

@@

The control rod worth (CRW) is the amount of negative reactivity that associated with the control rod insertion. The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of i$^{th}$ CR, $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion i$^{th}$ CR \cite{vcerba2017optimization}.
